Dancing on Water: The Choreography of Sulfur Dioxide Adsorption to Aqueous Surfaces

### 2011-07-05 EquilibratedOrientation.tex
Starting edits for final draft

The plots indicate that \suldiox~orients similarly at both the low and high concentration interfacial environments. The plots of $\phi$ for both concentrations exhibit isotropic distributions. However, the $\theta$ values follow similar trends at both concentrations indicating that the \suldiox~sulfur orients down towards the water phase, with both oxygens pointing away from the surface once the \suldiox~is within approx. 5\angs~of the surface. This behavior continues down to at least 5\angs~below the water surface location, notwithstanding any chemical reactions that may occur that are not simulated using the classical MD techniques utilized in this work.

>>>>

The plots indicate that \suldiox~orients similarly at both the low and high concentration interfacial environments. The plots of $\phi$ for both concentrations exhibit isotropic distributions. However, the $\theta$ values follow similar trends at both concentrations indicating that the \suldiox~sulfur orients down towards the water phase, with both oxygens pointing away from the surface once the \suldiox~is within approximately 5\angs~of the surface. This behavior continues down to at least 5\angs~below the water surface location, notwithstanding any chemical reactions that may occur that are not simulated using the classical MD techniques utilized in this work.
